Behavior Driven Development in Haskell

### 2012-06-01 paper.tex
BCP: Step 4: spec first, then implementation

So far, so good.  We have an implementaion of the Fibonacci function
that swiftly calculates correct values for all positive integers.
But what about negative ones? Our implementation uses the list index
operator {\tt (!!)} which is a partial function that throws an
exeption for negative indexes.  Let's specify that behaviour.

@@

\noindent Throwing exceptions from pure code is considered poor
design, so we guard the {\tt (!!)} operator against negative
indexes.

@@

\noindent This concludes our example coding session.  We have seen how
to utilize behavior driven development to incrementally build a small
library.  The combinators {\tt shouldBe}, {\tt shouldReturn} and {\tt
shouldThrow} can be used to specify behavior of functions in an
intuitive, easy to read manner.  The final version of our library
looks like this.

>>>>

So far, so good.  We have an implementaion of the Fibonacci function
that swiftly calculates correct values for all positive integers.
But what about negative ones? Let's assume that we want our
implementation to throw an exception in this case. We would
specify it like this.

@@

\noindent Our implementation already fulfils this spec, so we are
fine. Some time later however, the one person in our team that knows
more about Haskell than we do, convinces us that throwing exceptions
from pure code is considered poor design. Hence, we change the
specification so that zero should be the result for negative inputs.

@@

\noindent This concludes our example coding session.  We have seen how
to utilize behavior driven development to incrementally build a small
library.  We always extend or adapt the specification and watch it
fail first.  Then, we fix the implementation.  The combinators {\tt
shouldBe}, {\tt shouldReturn} and {\tt shouldThrow} can be used to
specify behavior of functions in an intuitive, easy to read manner.
The final version of our library looks like this.
